\pdftitle

### 2018-05-14 maxNt_v2.tex
V2

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2018-05-14T15:43:37+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

@@

In the final discussion we present some arguments in favour of one choice.

In the rest of the paper we mathematically formulate this dilemma. To this
purpose we also present some probability relations relevant to sampling.
The relations we present are well-known in survey sampling and in the
pedagogic problem of drawing from an urn without replacement, yet they are
somewhat hard to find explicitly written in the neuroscientific literature,
so they may be of interest on their own. We briefly discuss also two very
different meaning of \enquote{representative} that lead to similar initial
probability assignments for sampling.

@@

@@

@@

@@

>>>>

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2018-05-14T16:10:02+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

\hrule
\mynote{delete this part}

@@

In the final discussion we present some arguments in favour of one choice.
\hrule

In the rest of the paper we mathematically formulate and analyse the first
part of this dilemma, focusing on the derivation~\ref{item:entropic_prior}.
To this purpose we also present some probability relations relevant to
sampling. The relations we present are well-known in survey sampling and in
the pedagogic problem of drawing from an urn without replacement, yet they
are somewhat hard to find explicitly written in the neuroscientific
literature, so they may be of interest on their own. We briefly discuss
also two very different meaning of \enquote{representative} that lead to
similar initial probability assignments for sampling.

@@

\hrule

\mynote{DISCUSSION ABOUT THE SECOND STATE OF KNOWLEDGE IS TO BE DISCARDED}

@@

\hrule

@@

\begin{figure}[!t]
\centering
\includegraphics[width=0.9\linewidth]{newplot.pdf}
% 
\caption{\mynote{to be written} distributions obtained using
  formulae~\eqref{eq:app_maxent_pop_marg_unknown_N} and the other two}
\label{fig:newplot}
\end{figure}%maxent_pop_or_sample.nb

@@

\mynote{needs to be changed}
